---
title: "International Student Report"
author: "Team Diversity"
date: "SeoHyeong Jeong, Jolina Yao, Katarina Palermo, Jessica Chen, and QiMing Yeow"
output: 
  ioslides_presentation:
    fig_caption: yes
    fig_height: 3
    fig_width: 4.5
    smaller: yes
    widescreen: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DataComputing)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Introduction
<div class="columns-2">

**Questions**  

1. How will president, senate and house affect international students?    

2. Is there relationship between proportion of international students and college revenue?    

3. How will international students from the seven countries in the immigration executive order be affected under Trump administration? 

```{r data, echo = FALSE}
data_clean <- read.csv(file='data_clean.csv', header=TRUE, sep=",")
visa <- read.csv(file='visa_party_enrollment.csv', header=TRUE, sep=",")
visa <- visa %>% 
  mutate(IS=ifelse(grepl("Iran|Iraq|Syria|Sudan|Libya|Yemen|Somalia", Country), "Yes", "No")) %>%
  transform(F.1 = as.numeric(F.1),
            J.1 = as.numeric(J.1),
            M.1 = as.numeric(M.1),
            Total.Visas = as.numeric(Total.Visas))
```

**Methods**  

- UNIX, Web-Scrape, Data Wrangling  

- Data Visualization  

- Regression Analysis  

**Datasets**

Delta Cost Project Database  
  > *Time Period:* from 1987 to 2013  
  > *Variables:* Academic year, total enrollment, government funding, international students  

Visa   
  > *Time Period:* from 1997 to 2016  
  > *Variables:* F1, J1, M1, total visa, country, year  
  
Congress Data    
  > *Time Period:* from 1855 to 2015    
  > *Variables:* year, chamber, party status, seats    

Presidential Party (Web-Scrape)    
  > *Time Period:* from 1841 to 2017    
  > *Variables:* party, year   

</div>

## Results

```{r graphs, echo=FALSE, message=FALSE, error=FALSE}
# plots of college revenue/prop of internation students and president/house/senate
college_revenue_Pres <- data_clean %>%
  ggplot(aes(x = Academic_Year, y = Income_per_GDP, color = Party)) +
  geom_line(aes(color=Party, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=1.5, label= "Recession") + 
  labs(title = "College Revenue by Presidential Party",
       x = "Academic Year",
       y = "College Revenue (% of GDP)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 15)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) +
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")
#college_revenue_Pres

college_revenue_House <- data_clean %>%
  ggplot(aes(x = Academic_Year, y = Income_per_GDP, color = House)) +
  geom_line(aes(color=House, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=1.5, label= "Recession") + 
  labs(title = "College Revenue by Dominant Party in House",
       x = "Academic Year",
       y = "College Revenue (% of GDP)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 15)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) +
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")
#college_revenue_House

college_revenue_Senate <- data_clean %>%
  ggplot(aes(x = Academic_Year, y = Income_per_GDP, color = Senate)) +
  geom_line(aes(color=Senate, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=1.5, label= "Recession") + 
  labs(title = "College Revenue by Dominant Party in Senate",
       x = "Academic Year",
       y = "College Revenue (% of GDP)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 15)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) +
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")
#college_revenue_Senate

int_student_Pres <- data_clean %>%
  filter(Academic_Year != 1988, Academic_Year != 1990) %>% ## this line is to exclude 1988 and 1990
  ggplot(aes(x = Academic_Year, y = Prop_Intl_Student, color = Party)) +
  geom_line(aes(color=Party, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=3.6, label= "Recession") + 
  labs(title = "International Student by Presidential Party",
       x = "Academic Year",
       y = "International Student (% of total enrollment)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 13)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) +
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")

#int_student_Pres

int_student_House <- data_clean %>%
  filter(Academic_Year != 1988, Academic_Year != 1990) %>% ## this line is to exclude 1988 and 1990
  ggplot(aes(x = Academic_Year, y = Prop_Intl_Student, color = House)) +
  geom_line(aes(color=House, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=3.6, label= "Recession") + 
  labs(title = "International Student by Dominant Party in House",
       x = "Academic Year",
       y = "International Student (% of total enrollment)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 15, face = "bold"),
        axis.title = element_text(size = 13)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) + 
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")
#int_student_House

int_student_Senate <- data_clean %>%
  filter(Academic_Year != 1988, Academic_Year != 1990) %>% ## this line is to exclude 1988 and 1990
  ggplot(aes(x = Academic_Year, y = Prop_Intl_Student, color = Senate)) +
  geom_line(aes(color=Senate, group=1), size = 1.5) +
  annotate("text", x=1990.5, y=3.6, label= "Recession") + 
  labs(title = "International Student by Dominant Party in Senate",
       x = "Academic Year",
       y = "International Student (% of total enrollment)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(legend.position = c(0.9, 0.2), 
        legend.justification = c(0.9, 0.2),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 15, face = "bold"),
        axis.title = element_text(size = 13)) +
  annotate("rect", xmin=1990, xmax=1991, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3) + 
  scale_x_continuous(breaks = seq(min(data_clean$Academic_Year), max(data_clean$Academic_Year), by = 3), "Academic Year")
#int_student_Senate
```

```{r interactive}
##Code skeleton from Stack Overflow http://stackoverflow.com/questions/33469773/multiple-plots-in-r-shiny user: jenesaisquoi
makePlotContainers <- function(n, ncol=2, prefix="plot", height=225, width="100%", ...) {
    ## Validate inputs
    validateCssUnit(width)
    validateCssUnit(height)

    ## Construct plotOutputs
    lst <- lapply(seq.int(n), function(i)
        plotOutput(sprintf('%s_%g', prefix, i), height=height, width=width))

    ## Make columns
    lst <- lapply(split(lst, (seq.int(n)-1)%/%ncol), function(x) column(12/ncol, x))
    do.call(tagList, lst)
}

renderPlots <- function(n, input, output, prefix="plot") {
    for (i in seq.int(n)) {
        local({
            ii <- i  # need i evaluated here
            ## These would be your 10 plots instead
            output[[sprintf('%s_%g', prefix, ii)]] <- renderPlot({
                if (ii == 1) {
                  if (input$inter == "President") {
                  int_student_Pres
                } else if (input$inter == "House") {
                  int_student_House
                } else if (input$inter == "Senate"){
                  int_student_Senate
                }
              } else {
                  if (input$revenue == "President") {
                  college_revenue_Pres
                } else if (input$revenue == "House") {
                  college_revenue_House
                } else if (input$revenue == "Senate"){
                  college_revenue_Senate
                }
              }
            })
        })
    }
}

ui <- shinyUI(
    fluidPage(
        sidebarLayout(
            sidebarPanel(
                selectInput("inter", label = "Choose Government Institution to View Porportion of International Students by", choices=c("President", "House","Senate")),
                selectInput("revenue", label = "Choose Government Institution to View College Revenue by", choices=c("President", "House","Senate"))
            ),
            mainPanel(
                uiOutput('plots')
            )
        )
    )
)

server <- shinyServer(function(input, output) {
    output$plots <- renderUI({
        makePlotContainers(2, ncol=1)
    })
    observeEvent(2, renderPlots(2, input, output))
})

shinyApp(ui, server)
```


## Regression Analysis
1. `rpart(Prop_Intl_Student ~ Party + House + Senate, data_clean)`  
By plugging in Republican (the current political party) to all three variable, this model predicts that the proportion of international students is 3.234834%.

2. `lm(formula = Income_per_GDP ~ poly(Prop_Intl_Student, 2), data = data_clean)`  
Following the above findings, this model predicts that the college revenue generated per GDP is 1.160418%.

3. `lm(avgProp ~ president + Year, data=visa_prop)`  
The model predicts that in 2020 the number of international students from the seven countries in the immigration executive order is 0.004799307% of total enrollment.
```{r, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
p3 <- data_clean %>%
  ggplot(aes(x = Prop_Intl_Student, y = Income_per_GDP)) +
  geom_point() +
  geom_smooth( method = "loess", se = FALSE, col = "red") +
  scale_x_continuous(limits = c(2.5,3.75)) + 
  labs(title = "College Revenue vs Proportion of International Student",
    x = "Proportion of International Student (%)",
    y = "College Revenue per GDP (%)") +
    theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8, face = "italic"))
p3

point <- visa %>% 
  filter(IS=="Yes") %>%
  mutate(prop=((F.1+J.1+M.1)*100/Total_Enrollment)) %>%
  ggplot(aes(x=Year, y=prop)) +
  geom_point(aes(color=president)) +
  geom_smooth(method="loess", se = FALSE, col="red") +
  labs(title = "Average International Student Visa in Islamic States",
       x = "Academic Year",
       y = "F1, J1, M1 Visa Admission(% of total enrollment)") + 
  scale_color_manual(values=c(Democrat="#3366FF", Republican="#FF6633")) +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(size = 0.5, color = "Grey"),
        panel.grid.major.x = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 8, face = "italic")) +
  annotate("rect", xmin=2000.5, xmax=2001.5, ymin=-Inf, ymax=Inf, alpha=0.3) +
  annotate("rect", xmin=2008, xmax=2010, ymin=-Inf, ymax=Inf, alpha=0.3)


point
```

```{r}
reactive({
  if (!is.null(input$var1))
  setwd("/opt/shiny-server/samples/sample-apps/test")
  sink("outfile.txt")
  cat(input$var1)
  sink()
  })
```

